---
title: "Sike Data Challenge"
author: "Raghava Govil"
date: "10/26/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message = FALSE}
library(readr)
library(dplyr)
library(lubridate)
library(DT)
```

```{r message = FALSE}
#Importing the Data
data <- read_csv("Crime_Data_from_2010_to_Present.csv")
#Making a separate Dataframe for data pertaining to West LA
data2 <- as.data.frame(data[data$`Area Name`=="West LA",])
```

```{r}
#Number of crimes in different parts of LA
datatable(as.data.frame(table(data$`Area Name`) %>% sort()))
```

###All the following insights have been made using data pertaining only to West LA

```{r message = FALSE}
#Number of Different type of Crimes in West LA
datatable(as.data.frame((table(data2$`Crime Code Description`) %>% sort(decreasing = TRUE))))
```

```{r message = FALSE}
#Number of Crimes per Age group
#data2 = as.data.frame(data2)
sum(table(data2[which(data2[, 11] %in% c(0:18)), 9])) #0-18
sum(table(data2[which(data2[, 11] %in% c(19:30)), 9])) #19-30
sum(table(data2[which(data2[, 11] %in% c(31:50)), 9])) #31-50
sum(table(data2[which(data2[, 11] %in% c(51:99)), 9])) #50+
```

```{r message = FALSE}
data2$`Date Occurred` <- as.Date(data2$`Date Occurred`, format = "%m/%d/%Y")
data2$DOW <- wday(data2$`Date Occurred`) 
data2$month <- month(data2$`Date Occurred`) 
data2$year <- year(data2$`Date Occurred`)
data2$`Time Occurred` <- (as.numeric(data2$`Time Occurred`) %/% 100)
data2$`Time Occurred` <- as.character(data2$`Time Occurred`)
```

```{r message = FALSE}
#Number of Crimes occured at different times of the day
datatable(as.data.frame(table(data2$`Time Occurred`)))
```

```{r}
#Number of crimes per year
barplot(table(data2$year), main = "Number of Crimes in West LA per year", col = "black", xlab = "Year", ylim = c(0, 10000), ylab = "Number of Crimes")
```

```{r}
#Number of crimes affecting men and women
table(data2$`Victim Sex`)
```

```{r}
#Crime by premise Description
datatable(as.data.frame(table(data2$`Premise Description`) %>% sort(decreasing = TRUE)))
```

```{r}
#Burglary by premise description
datatable(as.data.frame(table(data2$`Premise Description`[data2$`Crime Code Description`=="BURGLARY"]) %>% sort(decreasing = TRUE)))
```

###Insights from the data:
####1. West LA seems to have the 4th lowest number of crimes in LA, making it relatively safe  
####2. Burglary is the most common crime in West LA  
####3. The age group 31-50 is the most affected by crime in West LA  
####4. Surprisingly, the maximum number of crimes occur at around 12 noon  
####5. There is no particular trend in the number of crimes over the years, but there has been a continuous drop in the number of crimes from 2015 to 2018  
####6. Males and females are affected almost equally, with males in the lead by a margin  
####7. Most of the crimes take place in Single Family Dwellings  
####8. Most of the burglaries too take place mostly in Single Family Dwellings  
